% This work by Jeremy A. Hansen is licensed under a Creative Commons 
% Attribution-NonCommercial-ShareAlike 3.0 Unported License, 
% as described at http://creativecommons.org/licenses/by-nc-sa/3.0/legalcode


In order to write code we must have a development environment. There are many sollutions to do this. 
Some can be as simple as having a text editor and a command line compiler and linker program. 
Another solution is to install a Integrated Development Environment (IDE). 
One of the most popular IDE's for C++ development is Visual Studio Community. 
Visual Studio Community is free and can be downloaded from the web. 
For those who can not use visual studio community we will also explain how to use Visual Studio Code
 which is also free but runs on Windows, Mac and Linux. In this chapter we will explain how to install 
 Visual Studio Community or Visual Studio Code as an IDE and will provide you instruction on how to 
 make a basic Hello World Application.

\LevelD{Visual Studio}
Visual studio is an IDE that can be used to code in multiple languages. It is primarily an IDE designed
to work on Microsoft Windows machines. You can see the system requirements Here:  
\url{https://docs.microsoft.com/en-us/visualstudio/releases/2019/system-requirements}

\LevelE{Downloading the software}
TODO: how to download visual studio

\LevelE{Configuring the software}
TODO: How to run visual studio configuration

\LevelE{Hello World}
TODO: Hello world walk through

\LevelD{Visual Studio Code}
TODO: About d visual studio code

\LevelE{Downloading the software}
TODO: How to download visual studio code

\LevelE{Configuring the software}
TODO: How to run visual studio configuration

\LevelE{Hello World}
TODO: Hello world walk through
	